Plasticity and adaptation to high light intensity amplify the advantage of amphistomous leaves

### 2025-07-25 ms/ms.tex
added model summary tables

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\usepackage{hyperref}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\newcommand{\aahigh}{\mathrm{AA}_{2000}}
\newcommand{\aalow}{\mathrm{AA}_{150}}
\newcommand{\aashade}{\mathrm{AA}_{\text{shade}}}
\newcommand{\aasun}{\mathrm{AA}_{\text{sun}}}
\newcommand{\aax}{$\mathrm{AA}$}
\newcommand{\aay}{\mathrm{AA}}
\newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
\newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
\newcommand{\agcurve}{$A \textendash g_\text{sw}$}
\newcommand{\aqcurve}{$A \textendash Q$}
\newcommand{\ca}{$C_\mathrm{a}$}
\newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\gias}{$g_\text{ias}$}
\newcommand{\gmax}{$g_\text{max}$}
\newcommand{\gmaxratio}{$g_\text{max,ratio}$}
\newcommand{\gmaxshade}{$g_\text{max,shade}$}
\newcommand{\gmaxsun}{$g_\text{max,sun}$}
\newcommand{\gsw}{$g_\text{sw}$}
\newcommand{\loggsw}{$\log(g_\text{sw})$}
\newcommand{\logA}{$\log(A)$}
\newcommand{\ppfd}{$\mathrm{PPFD}$}
\newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\rh}{$\mathrm{RH}$}
\newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
\newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

We fit Bayesian mixed effects models with phylogenetically structured
random effects to test predictions of competing hypotheses about why
amphistomy advantage (\aax) might be greater for leaves in sunny, open
habitats. We fit all models combinations of measurement light intensity,
growth light intensity, and their interaction as both fixed effects and
random effects among populations. In other words, we test whether there
were main effects of light intensity treatments and/or whether
populations varied in their response to light intensity treatments. In
all models, we included population as a phylogenetically structured
random effect. We accounted for uncertainty in \(\widehat{\mathrm{AA}}\)
using the standard deviation of the posterior distribution of each
\(\widehat{\mathrm{AA}}\) estimate (Section~\ref{sec-aa-est}). We
crossed fixed and random effect structures with fixed effects of
measurement light intensity and/or growth light intensity on the
distributional parameter, \(\sigma\), the residual variance in \aax{}.
In total, we fit 100 models, each with a different combination of fixed,
random, and distributional effects. We used the RAxML
whole-transcriptome concatenated phylogeny based on 2,745 100-kb genomic
windows from (\emph{64}). Two of our populations were not in this tree.
We used accession LA1044 in place of LA3909, two populations of \emph{S.
galapagnse}; LA0750 was added as sister to LA0716, two closely related
populations of \emph{S. pennellii}. The node separating LA0750 from
LA0716 was placed half-way between the next deepest node. We used the
leave-one-out cross-validation information criterion (LOOIC) to compare
the fit of models (\autoref{tbl-aa_loo1}) using the \emph{R} package
\textbf{loo} version 2.8.0 (\emph{65}) to calculate LOOIC values. We
selected the model with the lowest LOOIC value to generate posterior
predictions for hypothesis testing.

@@

@@

\includegraphics{ms_files/figure-pdf/fig-sr-rxnorm-1.pdf}

>>>>

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
    \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\makeatletter
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}{
    \@ifstar
      \xxxParagraphStar
      \xxxParagraphNoStar
  }
  \newcommand{\xxxParagraphStar}[1]{\oldparagraph*{#1}\mbox{}}
  \newcommand{\xxxParagraphNoStar}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}{
    \@ifstar
      \xxxSubParagraphStar
      \xxxSubParagraphNoStar
  }
  \newcommand{\xxxSubParagraphStar}[1]{\oldsubparagraph*{#1}\mbox{}}
  \newcommand{\xxxSubParagraphNoStar}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\makeatother

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother
% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\usepackage{hyperref}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\newcommand{\aahigh}{\mathrm{AA}_{2000}}
\newcommand{\aalow}{\mathrm{AA}_{150}}
\newcommand{\aashade}{\mathrm{AA}_{\text{shade}}}
\newcommand{\aasun}{\mathrm{AA}_{\text{sun}}}
\newcommand{\aax}{$\mathrm{AA}$}
\newcommand{\aay}{\mathrm{AA}}
\newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
\newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
\newcommand{\agcurve}{$A \textendash g_\text{sw}$}
\newcommand{\aqcurve}{$A \textendash Q$}
\newcommand{\ca}{$C_\mathrm{a}$}
\newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\gias}{$g_\text{ias}$}
\newcommand{\gmax}{$g_\text{max}$}
\newcommand{\gmaxratio}{$g_\text{max,ratio}$}
\newcommand{\gmaxshade}{$g_\text{max,shade}$}
\newcommand{\gmaxsun}{$g_\text{max,sun}$}
\newcommand{\gsw}{$g_\text{sw}$}
\newcommand{\loggsw}{$\log(g_\text{sw})$}
\newcommand{\logA}{$\log(A)$}
\newcommand{\ppfd}{$\mathrm{PPFD}$}
\newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\rh}{$\mathrm{RH}$}
\newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
\newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

\usepackage{bookmark}

@@

We fit Bayesian mixed effects models with phylogenetically structured
random effects to test predictions of competing hypotheses about why
amphistomy advantage (\aax) might be greater for leaves in sunny, open
habitats. We fit all models combinations of measurement light intensity,
growth light intensity, and their interaction as both fixed effects and
random effects among populations. In other words, we test whether there
were main effects of light intensity treatments and/or whether
populations varied in their response to light intensity treatments. In
all models, we included population as a phylogenetically structured
random effect. We accounted for uncertainty in \(\widehat{\mathrm{AA}}\)
using the standard deviation of the posterior distribution of each
\(\widehat{\mathrm{AA}}\) estimate (Section~\ref{sec-aa-est}). We
crossed fixed and random effect structures with fixed effects of
measurement light intensity and/or growth light intensity on the
distributional parameter, \(\sigma\), the residual variance in \aax{}.
We used a robust regression approach by assuming \(t\)-distributed
residuals, which makes estimates less susceptible to extreme values. In
total, we fit 100 models, each with a different combination of fixed,
random, and distributional effects. We used the RAxML
whole-transcriptome concatenated phylogeny based on 2,745 100-kb genomic
windows from (\emph{64}). Two of our populations were not in this tree.
We used accession LA1044 in place of LA3909, two populations of \emph{S.
galapagnse}; LA0750 was added as sister to LA0716, two closely related
populations of \emph{S. pennellii}. The node separating LA0750 from
LA0716 was placed half-way between the next deepest node. We used the
leave-one-out cross-validation information criterion (LOOIC) to compare
the fit of models (\autoref{tbl-aa_loo1}) using the \emph{R} package
\textbf{loo} version 2.8.0 (\emph{65}) to calculate LOOIC values. We
selected the model with the lowest LOOIC value to generate posterior
predictions for hypothesis testing.

@@

\caption{\label{tbl-fit_aa1}Parameter estimates and 95\% confidence
intervals (CIs) from the posterior distribution of the selected model.
Models potentially include fixed, random, and distributional effects of
growth light intensity (shade and sun), measurement light intensity (low
and high), and their interaction on amphistomy advantage
(\(\mathrm{AA}\)). The distributional effects refer to the effect of
factors on residual variation in \(\mathrm{AA}\), denoted \(\sigma\), on
a log-link scale. For phylogenetically structured random effects, we
report the estimated standard deviation (SD).}

\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{4in}>{\raggedright\arraybackslash}p{2in}}
\toprule
Parameter & Estimate [95\% CI]\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{Fixed effects}}\\
\hspace{1em}\cellcolor{gray!10}{$\mathrm{AA}$ intercept (shade, low light)} & \cellcolor{gray!10}{0.08 [0.01, 0.16]}\\
\hspace{1em}effect of sun on $\mathrm{AA}$ & 0.04 [-0.02, 0.12]\\
\hspace{1em}\cellcolor{gray!10}{effect of high light on $\mathrm{AA}$} & \cellcolor{gray!10}{-0.03 [-0.06, 0]}\\
\hspace{1em}effect of sun $\times$ high light interaction on $\mathrm{AA}$ & -0.03 [-0.1, 0.03]\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{Distributional parameters}}\\
\hspace{1em}\cellcolor{gray!10}{$\log \sigma$ intercept (shade, low light)} & \cellcolor{gray!10}{-2.51 [-2.61, -2.41]}\\
\hspace{1em}effect of sun on $\log \sigma$ & 0.23 [0.12, 0.33]\\
\hspace{1em}\cellcolor{gray!10}{effect of high light on $\log \sigma$} & \cellcolor{gray!10}{-0.19 [-0.3, -0.09]}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{Random effect SDs}}\\
\hspace{1em}$\mathrm{AA}$ among populations & 0.06 [0.04, 0.1]\\
\hspace{1em}\cellcolor{gray!10}{effect of sun on $\mathrm{AA}$ among populations} & \cellcolor{gray!10}{0.05 [0, 0.1]}\\
\hspace{1em}effect of high light on $\mathrm{AA}$ among populations & 0.02 [0, 0.05]\\
\hspace{1em}\cellcolor{gray!10}{effect of sun $\times$ high light interaction on $\mathrm{AA}$ among populations} & \cellcolor{gray!10}{0.04 [0, 0.1]}\\
\bottomrule
\end{tabular}

\caption{\label{tbl-fit_aa2}Parameter estimates and 95\% confidence
intervals (CIs) from the posterior distribution of the selected model
with leaf mass per area (LMA) as potential mediator variable. Models
potentially include fixed, random, and distributional effects of growth
light intensity (shade and sun), measurement light intensity (low and
high), \(\log \mathrm{LMA}\), and their interactions on amphistomy
advantage (\(\mathrm{AA}\)). The distributional effects refer to the
effect of factors on residual variation in \(\mathrm{AA}\), denoted
\(\sigma\), on a log-link scale. LMA can also be affected by growth
light intensity and population. For phylogenetically structured random
effects, we report the estimated standard deviation (SD).}

\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{4.5in}>{\raggedright\arraybackslash}p{2in}}
\toprule
Parameter & Estimate [95\% CI]\\
\midrule
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Response: $\mathrm{AA}$}}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{~~Fixed effects}}\\
\hspace{1em}\hspace{1em}\cellcolor{gray!10}{$\mathrm{AA}$ intercept (shade, low light)} & \cellcolor{gray!10}{-0.01 [-0.12, 0.09]}\\
\hspace{1em}\hspace{1em}effect of sun on $\mathrm{AA}$ & 0.01 [-0.05, 0.06]\\
\hspace{1em}\hspace{1em}\cellcolor{gray!10}{effect of high light on $\mathrm{AA}$} & \cellcolor{gray!10}{-0.03 [-0.07, 0]}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{~~Distributional parameters}}\\
\hspace{1em}\hspace{1em}$\log \sigma$ intercept (shade, low light) & -2.5 [-2.61, -2.4]\\
\hspace{1em}\hspace{1em}\cellcolor{gray!10}{effect of sun on $\log \sigma$} & \cellcolor{gray!10}{0.23 [0.13, 0.34]}\\
\hspace{1em}\hspace{1em}effect of high light on $\log \sigma$ & -0.19 [-0.29, -0.08]\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{~~Random effect SDs}}\\
\hspace{1em}\hspace{1em}\cellcolor{gray!10}{$\mathrm{AA}$ among populations} & \cellcolor{gray!10}{0.06 [0.04, 0.1]}\\
\hspace{1em}\hspace{1em}effect of sun on $\mathrm{AA}$ among populations & 0.04 [0, 0.1]\\
\hspace{1em}\hspace{1em}\cellcolor{gray!10}{effect of high light on $\mathrm{AA}$ among populations} & \cellcolor{gray!10}{0.02 [0, 0.05]}\\
\hspace{1em}\hspace{1em}effect of sun $\times$ high light interaction on $\mathrm{AA}$ among populations & 0.04 [0, 0.09]\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textbf{Response: $\log~\mathrm{LMA}$}}\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{~~Fixed effects}}\\
\hspace{1em}\hspace{1em}\cellcolor{gray!10}{$\log \mathrm{LMA}$ intercept (shade)} & \cellcolor{gray!10}{2.99 [2.42, 3.52]}\\
\hspace{1em}\hspace{1em}effect of sun on $\log \mathrm{LMA}$ & 0.8 [0.36, 1.27]\\
\addlinespace[0.3em]
\multicolumn{2}{l}{\textit{~~Random effect SDs}}\\
\hspace{1em}\hspace{1em}\cellcolor{gray!10}{$\log \mathrm{LMA}$ among populations} & \cellcolor{gray!10}{0.48 [0.35, 0.66]}\\
\hspace{1em}\hspace{1em}effect of sun on $\log \mathrm{LMA}$ among populations & 0.37 [0.23, 0.6]\\
\bottomrule
\end{tabular}

@@

\pandocbounded{\includegraphics[keepaspectratio]{ms_files/figure-pdf/fig-sr-rxnorm-1.pdf}}
